Fast and scalable Gaussian process modeling with applications to astronomical time series \vspace{-3\baselineskip}

### 2017-03-15 paper/ms.tex
some words about real examples and captions

In this example, we inject the signal of a simulated exoplanet transit into a
real \kepler\ light curve and then demonstrate that we can recover the true
physical parameters of the exoplanet while modeling the stellar variability
using \celerite.
This example is different from all the previous examples because in this case,
we are uninterested in the inferred parameters of the covariance model.
Instead, we're interested in inferring constraints on the parameters of the
mean model.
In \eq{gp-likelihood} these parameters are called $\bvec{\theta}$ and in this
example, the mean function $\mu_\bvec{\theta}(t)$ is a limb-darkened transit
light curve \dfmtodo{CITE MA} parameterized by a period $P$, a transit
duration $T$, a phase or epoch $t_0$, an impact parameter $b$, the radius
of the planet in units of the stellar radius $R_P/R_\star$, and several
parameters describing the limb-darkening profile of the star \dfmtodo{CITE}.

KIC~1430163 with simulated transit.
\Figure{transit-ml} and \Figure{transit-corner}.

\begin{figure}[!htbp]
\begin{center}
\includegraphics[width=\textwidth]{figures/transit-ml.pdf}
\caption{\figurelabel{transit-ml}}
\end{center}
\end{figure}

\begin{figure}[!htbp]
\begin{center}
\includegraphics[width=\textwidth]{figures/transit-corner.pdf}
\caption{\figurelabel{transit-corner}}
\end{center}
\end{figure}

>>>>

In this example, we inject the signal of a simulated exoplanet transit into a
real \kepler\ light curve and then demonstrate that we can recover the true
physical parameters of the exoplanet while modeling the stellar variability
using \celerite.
This example is different from all the previous examples because in this case,
we are uninterested in the inferred parameters of the covariance model.
Instead, we're interested in inferring constraints on the parameters of the
mean model.
In \eq{gp-likelihood} these parameters are called $\bvec{\theta}$ and in this
example, the mean function $\mu_\bvec{\theta}(t)$ is a limb-darkened transit
light curve \dfmtodo{CITE MA} parameterized by a period $P$, a transit
duration $T$, a phase or epoch $t_0$, an impact parameter $b$, the radius
of the planet in units of the stellar radius $R_P/R_\star$, and several
parameters describing the limb-darkening profile of the star \dfmtodo{CITE}.
As in the previous example, we model the stellar variability using a GP model
with a kernel given by \eq{rot-kernel}.

To demonstrate this example, we take a month-long segment of the \kepler\
light curve for KIC~1430163~--~the target from the previous example~--~and
multiply it by a simulated transit model with known parameters.
The top panel of \Figure{transit-ml} shows the data including the simulated
transit.
The bottom panel shows the same data with the maximum likelihood prediction
for the stellar variation subtracted.
To find this model, we maximized the likelihood function in \eq{gp-likelihood}
with respect to the transit parameters $\bvec{\theta}$ and the variability
parameters $\bvec{\alpha}$ simultaneously.
\Figure{transit-corner} shows the marginalized posterior constraints on the
physical properties of the planet compared to the true values.
This procedure produces estimates of the planet parameters that are consistent
with the true values using \celerite\ as an effective model for the stellar
variability.

\begin{figure}[!htbp]
\begin{center}
\includegraphics[width=\textwidth]{figures/transit-ml.pdf}
    \caption{\emph{(top)} A month-long segment of \kepler\ light curve for
    KIC~1430163 with a synthetic transit model injected (black points) and the
    maximum likelihood model for the stellar variability and the transit model
    (blue line).
    \emph{(bottom)} The maximum likelihood ``de-trendeding'' of the data in
    the top panel.
    In this panel, the maximum likelihood model for the stellar variability
    has been subtracted to leave only the transits.
    The de-trended light curve is shown by black error bars and the maximum
    likelihood transit model is shown as a blue line.
    \figurelabel{transit-ml}}
\end{center}
\end{figure}

\begin{figure}[!htbp]
\begin{center}
\includegraphics[width=\textwidth]{figures/transit-corner.pdf}
\caption{The marginalized posterior constraints on the physical parameters of
    the planet transiting during the light curve shown in the top panel of
    \Figure{transit-ml}.
    The two-dimensional contours show the 0.5-, 1-, 1.5, and 2-sigma credible
    regions in the marginalized planes and the histograms along the diagonal
    show the marginalized posterior for each parameter.
    The true values used in the simulation are indicated by blue lines.
    For each parameter, the inference is consistent with the true value.
    \figurelabel{transit-corner}}
\end{center}
\end{figure}
